\cvsection{Work Experience}

\begin{cventries}
	\cventrytwopositions
	{Software Engineer 2}
	{Quotient Technology}
	{Benguluru, India}
	{Nov 2020 - present}
	{
		\begin{cvitems}
			\item {Extensive work on improving accessibility across all projects, was the go-to person for a11y in a team of 20.}
			\item {Worked on designing and implementing a WYSIWYG CMS app for retailer marketing campaigns (QEM).}
			\item {Worked on adding features to 2 e-commerce apps (Server side rendered React - O2, Genie).}
			\item {Mentored interns, and worked with stakeholders across different time zones.}
		\end{cvitems}
	}
	{Software Engineer 1, Intern}
	{Jan 2018 - Oct 2020}
	{
		\begin{cvitems}
			\item {Added features and improved performance in multiple React-based and jQuery-based applications.}
			\item {Implemented redesign of UI across multiple apps; Implemented all of frontend for a major project that has Millions of users today (text2rebate).}
			\item {Aided in the switch of the tech stack of a large project from dustjs-jQuery to React.}
			\item {Wrote clean, readable code and made sure to have 100\% unit test coverage in the APIs I implemented. Refactored a lot of code in a 8-year old project.}
		\end{cvitems}
	}
	    
	\cventry
	{Intern}
	{Goalwise}
	{Benguluru, India}
	{May 2017 - Jul 17}
	{
		\begin{cvitems}
			\item {Created and deployed a website to grade Mutual Funds’ Consolidated Account Summary portfolios.}
			\item {Automated days worth of manual work.}
		\end{cvitems}
	}
\end{cventries}